Transforming Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix

### 2018-04-19 rfinaldoc/JMR-17-1184-paper.tex
final2

H.S.M. Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and
translation of the tetrahedra by showing the
rotation is:
\begin{equation}
\theta_{bc} = \arccos(-2/3) 
\end{equation}
and the translation:
\begin{equation}
h_{bc} = 1/\sqrt{10}.
\end{equation}

Note that $\theta_{bc}$ is approximately $0.37 \cdot 2 \pi$ radians or  $131.81$ degrees.
The angle $\theta_{bc}$ is the rotation of \emph{each} tetrahedron, not the tetrahedra along a rail.  In \cref{fig:closeup},
each tetrahedron has either a yellow, blue, or red outer edge or rail.
That is, a blue-rail tetrahedron is rotated slightly more than a $1/3$ of a revolution to match the face of the yellow tetrahedron.

R.W. Gray's website\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in a more accessible form, gives the Cartesian coordinates in the form: $\begin{bmatrix}
           x \\
           y \\
           z
         \end{bmatrix}$
for a counter-clockwise BC helix in a right-handed coordinate system:
\begin{equation}
  \label{graycoxeter}
\vec{V}(n) =
\left [
  \begin{tabular}{c}
   $ r_{bc} \cos{n \theta_{bc}} $\\
   $ r_{bc} \sin{n \theta_{bc}} $\\
   $ n h_{bc}  $
  \end{tabular}
  \right ],
\text{ \qquad where: \qquad}
  \begin{tabular}{l}
 $ r_{bc} = \frac{3\sqrt{3}}{10} \approx 0.5196 $,\\
 $ h_{bc} = 1/\sqrt{10} \approx 0.3162 $, and \\
 $ \theta_{bc} = \arccos(-2/3) $  \text{,}\\
  \end{tabular}      
\end{equation}

and $n$ represents each integer numbered vertex in succession on the $z$-axis.

@@

Such a helix can be written:
\begin{equation}
  \label{eq:colored}
 \vec{H}_{BCcolored}(n,c) =
\left [
  \begin{tabular}{c}
   $ r_{bc}  \cos{((3 \theta_{bc} - 2 \pi)n + c  \theta_{bc})}  $\\
   $ r_{bc} \sin{((3 \theta_{bc} - 2 \pi)n + c  \theta_{bc})} $\\
   $ 3 h_{bc} (n + c/3)  $
  \end{tabular}
  \right ],
\text{ \qquad where:  \qquad}
  \begin{tabular}{l}
 $ r_{bc} = \frac{3\sqrt{3}}{10} $,\\
 $ h_{bc} = 1/\sqrt{10} $, and \\
 $ \theta_{bc} = \arccos(-2/3) $ \text{.}\\
  \end{tabular}      
\end{equation}

In this formula, integer values of $n$ may be taken as a vertex number for one rail and used to compute
its Cartesian
coordinates. Allowing $n$ to take non-integer values defines a continuous
helix in space which is close to the segmented polyline of the outer
tetrahedra edges, and equals them at integer
values.

@@

Thus, starting with the expression:
\begin{align*}
  c \theta_{bc} 
\end{align*}
introduce 3 into the denominator...
\begin{align*}
  (c/3)  (3 \theta_{bc}) 
\end{align*}
seeking $2\pi$ in the numerator, add canceling terms...
\begin{align*}
  (c/ 3) ((3 \theta_{bc} - 2 \pi)  + 2 \pi) 
\end{align*}
...and then use the definition of $\rho_{bc}$
\begin{align*}
  (c / 3) \rho_{bc}  + c 2 \pi /3 
\end{align*}
to finally obtain:
\begin{equation}
  c  ( \rho_{bc} +  2 \pi) /3  \text{.}
\end{equation}

This allows \cref{eq:colored} to be rewritten:

%% Actually, I am not sure if this is a clearer formulation...it might be, and need to put it in general!!!
\begin{equation}
\vec{H}_{BCcolored}(n,c) =
\left [
  \begin{tabular}{c}
    $ r  \cos{\rho_{bc} n + c (\rho_{bc} +  2 \pi) /3} $\\
   $ r  \sin{\rho_{bc} n + c (\rho_{bc} +  2 \pi) /3} $\\
   $ (n+c/3)  h_{bc} $
  \end{tabular}
  \right ],
\text{\qquad where: \qquad}
  \begin{tabular}{l}
%%  $\kappa = n + c/3$ \\
    $\rho_{bc} = (3 \theta_{bc} - 2 \pi)$, and \\
    $ h_{bc} = 1/\sqrt{10} $. \\    
  \end{tabular}      
\end{equation}

Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued).
It can now be asserted that in \cref{fig:helixcomparison} the black helix winds at
$\frac{3 \theta_{bc}}{\rho_{bc}} \approx 11.16 $ times the rate of a rail helix.

@@

The \emph{pitch} of any tetrahelix, defined as the axial length of a complete revolution
where $\rho \neq 0$ is:
\begin{equation}
  \label{pitcheqn}
p(\rho) = \frac{2 \pi  d}{\rho} \text{.}
\end{equation}

The pitch of the Boerdijk-Coxeter helix of edge length $1$ is the length of three tetrahedra times
$p(\rho_{bc})$:
\begin{equation}
   \frac{3 h_{bc}  2 \pi }{\rho_{bc}} 
   = \frac{6 \pi}{\sqrt{10}\rho_{bc}}
   \approx 9.64
 \text{.}
\end{equation}

The pitch is less than the number of tetrahedra because the tetrahedra
edges are not parallel to the axis of the tetrahelix.  It is a famous and interesting result
that the pitch is irrational. A BC helix never has two tetrahedra at
precisely the same orientation around the $z$-axis. However, this is
inconvenient to designers, who might prefer a rational pitch.
The idea of developing a rational period by arranging solid tetrahedra by relaxing
the face-to-face matching
has been explored\cite{sadler2013periodic}. 
The next sections develop slightly irregular edge lengths that support, for example,
a pitch of precisely 12
tetrahedra in one revolution which would allow an architect to
design a pleasing column having the top and bottom tetrahedra in the same relationship to the
viewer on both the capital and the basis.

@@

The ratio of the longest member in a testrahelix to the shortest is:
\begin{equation}
R(T) = \frac{\max \{T(n_1,n_2) | n_1,n_2 \in \mathbb{Z} \}}{\min \{T(n_1,n_2) | n_1,n_2 \in \mathbb{Z} \}}
\label{eq:optdef}
\end{equation}

 The ratio of the BC helix is 1: $ R(H_{BC}) = 1$.

@@

\Cref{thm:pitchandparallel} justifies talking about the singular
\emph{pitch} of 
the optimal tetrahelix as the pitch of its three rail helices $(R,B,Y)$, even though there are
three such helices of equivalent pitch.
Since the axes of helices of any physical tetrahelix are parallel, take
them to be parallel to the $z$ axis. Define the radius of the tetrahelix:
\begin{align*}
rad(T) = \text{the radius of the smallest cylinder which contains all of nodes of the tetrahelix } T
\end{align*}
Define a \emph{minimax edge-length optimal tetrahelix} or just an
\emph{optimal tetrahelix} to be a tetrahelix for which there exists
no other tetrahelix  of the same radius with lower ratio of longest edge length to
shortest edge length
\begin{equation}
  OPT(T) \equiv \neg (\exists S : R(S) < R(T) \wedge rad(S) = rad(T))
  \label{eq:optdef}
\end{equation}

\begin{lemma}
  A tetrahelix where all points lie on the same line is not optimal.
    \label{lemma:notpoint}
\end{lemma}
\begin{proof}
As a little lemma for the proof below, observe that a tetrahelix $T$ of zero radius, where
all points lie on the same line,
is not as optimal as a tetrahelix of a small radius. The edges between rails $(R,B,Y)$ will be
shorter than the rail edges, and moving them apart slightly to form $T'$ lengthens the between-edge
rails, improving the ratios, so $R(T') < R(T)$.
\end{proof}

@@

Rewriting our formulation in terms of $\rho$:
\begin{equation}
  \begin{split}
  \label{eq:general}  
\vec{H}_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho}) =  
 \left [
  \begin{tabular}{c}
   $ r_{\rho} \cos(\chi \cdot (n \rho + c(\rho +  2 \pi) /3)) $\\
   $ r_{\rho}  \sin(\chi \cdot (n \rho + c(\rho +  2 \pi) /3)) $\\
   $ d_{\rho} (n + c /3) $
  \end{tabular}
  \right ] \\
   \end{split}
\text{\qquad where: } 
\begin{tabular}{l}
  $   1 = d_{\rho}^2 + 4 r_{\rho}^2 (\sin{ \rho / 2})^2 $, and \\
    $\chi \in \{-1,1\}$ \text{.} \\  
\end{tabular}
\end{equation}

$\vec{H}_{general}$ forces the user to select three values satisfying \cref{railangle}: $\rho$, $r_{\rho}$, and $d_{\rho}$.

@@

This syntax just represents the Euclidean distance between vertices. Thus:
\begin{equation}
%%  \text{one-hop} &= dist(\vec{H}_{general}(0,0,\rho,d_{\rho}),\vec{H}_{general}(0,1,\rho,d_{\rho},r))  \\  
%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r\sin(0) - r\sin(\rho/3+1\cdot\frac{2\pi}{3}))^2  +
%%    (r\cos(0) - r\cos(\rho/3 + 1\cdot\frac{2\pi}{3}))^2} \\
%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r\sin(\rho/3 + \frac{2\pi}{3}))^2  +
%%    (r - r\cos(\rho/3 + \frac{2\pi}{3}))^2} \\
%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r^2\sin^2(\rho/3 + \frac{2\pi}{3})  +
%%    r^2(1 - \cos(\rho/3 + \frac{2\pi}{3}))^2} \\
  %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.
  \text{one-hop}  = \sqrt{\frac{d_{\rho}^2}{9} + r^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \text{\qquad where: \qquad}   d_{\rho}^2 = 1 - 4 r^2 (\sin( \rho / 2)^2.
\end{equation}

%% so we substitute:
%% \begin{align*}
%%   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.  
%%   \text{one-hop}  &= \sqrt{\frac{1}{9}  + r^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \text{.}\\
%%   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.    
%% \end{align*}

By similar algebra and trigonometry:
\begin{equation}
  \text{two-hop}  = \sqrt{\frac{4 d_{\rho}^2}{9} +  r^2(\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \text{.}\\
\end{equation}

By definition of minimax edge length optimality \cref{eq:optdef}, we are trying to minimize:
\[
R(T(r)) = \frac{\max{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}}{\min{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}} \text{.}
\]
But since $\text{two-hop}(r) \geq \text{one-hop}(r)$, this is equivalent to:
\[
R(T(r)) =  \frac{   \max \{1,\text{two-hop}(r)\}}
      {   \min \{1,\text{one-hop}(r)\}} \text{.}
\]
This quantity will be equal to one of:
\begin{equation}
  \frac{\text{two-hop}(r)}{1},
\frac{1}{\text{one-hop}(r)},
\frac{\text{two-hop}(r)}{\text{one-hop}(r)} \text{.}
\label{eq:ratioset}
\end{equation}

We know that both one-hop($r$) and two-hop($r$) increase monotonically and continuously with increasing $r$.
By inspection, it seems likely that we will minimize this set by equating $\text{one-hop}(r)$ or $\text{two-hop}(r)$
to 1, but to be absolutely sure and to decide which one, we must examine the partial derivative of the ratio
 $\frac{\text{two-hop}(r)}{\text{one-hop}(r)}$ in this range.

@@

Let:
\begin{equation}
  f_{\rho} = -\frac{4 (\sin^2( \rho / 2))}{9} \text{,}
  \end{equation}
\begin{equation}
  g_{\rho} = -\frac{16 (\sin^2( \rho / 2))}{9} \text{,}
\end{equation}
\begin{equation}
  j_{\rho} = \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2 \text{,}
\end{equation}
and:
\begin{equation}
  k_{\rho} = \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2 \text{.}
\end{equation}

Then:
\begin{equation}
  \begin{split}
  \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}  &=
  \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ k_{\rho})}}
       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+j_{\rho}) }} \text{.}
  \end{split}       
\end{equation}

  By inspection of the graph of the derivative of this ratio rendered in \cref{fig:partialderivativediagram}
  observe that the partial derivative of this with respect to
radius $r$ is always negative, for any $\rho \leq \rho_{bc}$.

@@

Therefore, one decreases the minimax length
of the whole system as the radius increases
up to the point that the shorter, one-hop distance is equal to the rail-length, $1$.
In order to optimize the whole system so long as $\rho \leq \rho_{bc}$,
equate one-hop to $1$ to find the optimum radius:

\begin{equation}
  1 =  \sqrt{
      \frac{1}{9}   +   r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} \; \;+ \sin^2(\rho/3+ \frac{2\pi}{3}) + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2) 
    }
\end{equation}    
from which it follows that:

\begin{equation}
  r_{opt} = \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }} \text{ .} \numberthis  \label{eqrhoopt}
\end{equation}

This leads to a formula for $ d_{opt} $ computed from $\rho, r_{opt}$ via the rail angle equation \cref{railangle}:

\begin{equation}
  %%  d_{opt}^2 &= 1 - 4 (\frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }})^2 (\sin{ \rho / 2})^2   \\
  d_{opt}^2 = 1 - 4 (r_{opt})^2 (\sin{ \rho / 2})^2,
\end{equation}
which is expanded to:
\begin{equation}
%%  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
  d_{opt}^2 = 1 - \frac{16(\sin{ \rho / 2})^2}{\frac{9}{2} ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
\end{equation}
and then rewrite:
\begin{equation}
%%  d_{opt}^2 &= 1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
    d_{opt} = \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + \frac{9}{2} ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}  \text{ .}  \numberthis  \label{dopt}  \\      
\end{equation}

Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, one can
construct a minimax optimal tetrahelix where $0 \leq \rho \leq \rho_{bc}$.
%% Add here references to these equations.
\end{proof}

@@

\begin{corollary}
  The equitetrabeam with minimum maximum edge ratio is produced
  \newline by $\vec{H}_{general}$ when $ r = \sqrt{\frac{8}{27}} $ and the longest member is $\frac{2}{\sqrt{3}}$,
  which is less than $16\%$ longer
  than the shortest member.
\end{corollary}

>>>>

H.S.M. Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and
translation of the tetrahedra by showing the
rotation is:
\begin{equation}
\theta_{bc} = \arccos(-2/3) 
\end{equation}
and the translation:
\begin{equation}
h_{bc} = 1/\sqrt{10}.
\end{equation}
Note that $\theta_{bc}$ is approximately $0.37 \cdot 2 \pi$ radians or  $131.81$ degrees.
The angle $\theta_{bc}$ is the rotation of \emph{each} tetrahedron, not the tetrahedra along a rail.  In \cref{fig:closeup},
each tetrahedron has either a yellow, blue, or red outer edge or rail.
That is, a blue-rail tetrahedron is rotated slightly more than a $1/3$ of a revolution to match the face of the yellow tetrahedron.

R.W. Gray's website\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in a more accessible form, gives the Cartesian coordinates in the form: $\begin{bmatrix}
           x \\
           y \\
           z
         \end{bmatrix}$
for a counter-clockwise BC helix in a right-handed coordinate system:
\begin{equation}
  \label{graycoxeter}
\vec{V}(n) =
\left [
  \begin{tabular}{c}
   $ r_{bc} \cos{n \theta_{bc}} $\\
   $ r_{bc} \sin{n \theta_{bc}} $\\
   $ n h_{bc}  $
  \end{tabular}
  \right ],
\text{ \qquad where: \qquad}
  \begin{tabular}{l}
 $ r_{bc} = \frac{3\sqrt{3}}{10} \approx 0.5196 $,\\
 $ h_{bc} = 1/\sqrt{10} \approx 0.3162 $, and \\
 $ \theta_{bc} = \arccos(-2/3) $  \text{,}\\
  \end{tabular}      
\end{equation}
and $n$ represents each integer numbered vertex in succession on the $z$-axis.

@@

Such a helix can be written:
\begin{equation}
  \label{eq:colored}
 \vec{H}_{BCcolored}(n,c) =
\left [
  \begin{tabular}{c}
   $ r_{bc}  \cos{((3 \theta_{bc} - 2 \pi)n + c  \theta_{bc})}  $\\
   $ r_{bc} \sin{((3 \theta_{bc} - 2 \pi)n + c  \theta_{bc})} $\\
   $ 3 h_{bc} (n + c/3)  $
  \end{tabular}
  \right ],
\text{ \qquad where:  \qquad}
  \begin{tabular}{l}
 $ r_{bc} = \frac{3\sqrt{3}}{10} $,\\
 $ h_{bc} = 1/\sqrt{10} $, and \\
 $ \theta_{bc} = \arccos(-2/3) $ \text{.}\\
  \end{tabular}      
\end{equation}
In this formula, integer values of $n$ may be taken as a vertex number for one rail and used to compute
its Cartesian
coordinates. Allowing $n$ to take non-integer values defines a continuous
helix in space which is close to the segmented polyline of the outer
tetrahedra edges, and equals them at integer
values.

@@

Thus, starting with the expression:
\begin{align*}
  c \theta_{bc} 
\end{align*}
introduce 3 into the denominator...
\begin{align*}
  (c/3)  (3 \theta_{bc}) 
\end{align*}
seeking $2\pi$ in the numerator, add canceling terms...
\begin{align*}
  (c/ 3) ((3 \theta_{bc} - 2 \pi)  + 2 \pi) 
\end{align*}
...and then use the definition of $\rho_{bc}$
\begin{align*}
  (c / 3) \rho_{bc}  + c 2 \pi /3 
\end{align*}
to finally obtain:
\begin{equation}
  c  ( \rho_{bc} +  2 \pi) /3  \text{.}
\end{equation}  
This allows \cref{eq:colored} to be rewritten:
%% Actually, I am not sure if this is a clearer formulation...it might be, and need to put it in general!!!
\begin{equation}
\vec{H}_{BCcolored}(n,c) =
\left [
  \begin{tabular}{c}
    $ r  \cos{\rho_{bc} n + c (\rho_{bc} +  2 \pi) /3} $\\
   $ r  \sin{\rho_{bc} n + c (\rho_{bc} +  2 \pi) /3} $\\
   $ (n+c/3)  h_{bc} $
  \end{tabular}
  \right ],
\text{\qquad where: \qquad}
  \begin{tabular}{l}
%%  $\kappa = n + c/3$ \\
    $\rho_{bc} = (3 \theta_{bc} - 2 \pi)$, and \\
    $ h_{bc} = 1/\sqrt{10} $. \\    
  \end{tabular}      
\end{equation}
Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued).
It can now be asserted that in \cref{fig:helixcomparison} the black helix winds at
$\frac{3 \theta_{bc}}{\rho_{bc}} \approx 11.16 $ times the rate of a rail helix.

@@

The \emph{pitch} of any tetrahelix, defined as the axial length of a complete revolution
where $\rho \neq 0$ is:
\begin{equation}
  \label{pitcheqn}
p(\rho) = \frac{2 \pi  d}{\rho} \text{.}
\end{equation}
The pitch of the Boerdijk-Coxeter helix of edge length $1$ is the length of three tetrahedra times
$p(\rho_{bc})$:
\begin{equation}
   \frac{3 h_{bc}  2 \pi }{\rho_{bc}} 
   = \frac{6 \pi}{\sqrt{10}\rho_{bc}}
   \approx 9.64
 \text{.}
\end{equation}
The pitch is less than the number of tetrahedra because the tetrahedra
edges are not parallel to the axis of the tetrahelix.  It is a famous and interesting result
that the pitch is irrational. A BC helix never has two tetrahedra at
precisely the same orientation around the $z$-axis. However, this is
inconvenient to designers, who might prefer a rational pitch.
The idea of developing a rational period by arranging solid tetrahedra by relaxing
the face-to-face matching
has been explored\cite{sadler2013periodic}. 
The next sections develop slightly irregular edge lengths that support, for example,
a pitch of precisely 12
tetrahedra in one revolution which would allow an architect to
design a pleasing column having the top and bottom tetrahedra in the same relationship to the
viewer on both the capital and the basis.

@@

The ratio of the longest member in a testrahelix to the shortest is:
\begin{equation}
R(T) = \frac{\max \{T(n_1,n_2) | n_1,n_2 \in \mathbb{Z} \}}{\min \{T(n_1,n_2) | n_1,n_2 \in \mathbb{Z} \}}
\label{eq:optdef}
\end{equation}
 The ratio of the BC helix is 1: $ R(H_{BC}) = 1$.

@@

\Cref{thm:pitchandparallel} justifies talking about the singular
\emph{pitch} of 
the optimal tetrahelix as the pitch of its three rail helices $(R,B,Y)$, even though there are
three such helices of equivalent pitch.
Since the axes of helices of any physical tetrahelix are parallel, take
them to be parallel to the $z$ axis. Define the radius of the tetrahelix:
\begin{align*}
rad(T) = \text{the radius of the smallest cylinder which contains all of nodes of the tetrahelix } T
\end{align*}
Define a \emph{minimax edge-length optimal tetrahelix} or just an
\emph{optimal tetrahelix} to be a tetrahelix for which there exists
no other tetrahelix  of the same radius with lower ratio of longest edge length to
shortest edge length
\begin{equation}
  OPT(T) \equiv \neg (\exists S : R(S) < R(T) \wedge rad(S) = rad(T))
  \label{eq:optdef}
\end{equation}
\begin{lemma}
  A tetrahelix where all points lie on the same line is not optimal.
    \label{lemma:notpoint}
\end{lemma}
\begin{proof}
As a little lemma for the proof below, observe that a tetrahelix $T$ of zero radius, where
all points lie on the same line,
is not as optimal as a tetrahelix of a small radius. The edges between rails $(R,B,Y)$ will be
shorter than the rail edges, and moving them apart slightly to form $T'$ lengthens the between-edge
rails, improving the ratios, so $R(T') < R(T)$.
\end{proof}

@@

Rewriting our formulation in terms of $\rho$:
\begin{equation}
  \begin{split}
  \label{eq:general}  
\vec{H}_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho}) =  
 \left [
  \begin{tabular}{c}
   $ r_{\rho} \cos(\chi \cdot (n \rho + c(\rho +  2 \pi) /3)) $\\
   $ r_{\rho}  \sin(\chi \cdot (n \rho + c(\rho +  2 \pi) /3)) $\\
   $ d_{\rho} (n + c /3) $
  \end{tabular}
  \right ] \\
   \end{split}
\text{\qquad where: } 
\begin{tabular}{l}
  $   1 = d_{\rho}^2 + 4 r_{\rho}^2 (\sin{ \rho / 2})^2 $, and \\
    $\chi \in \{-1,1\}$ \text{.} \\  
\end{tabular}
\end{equation}  
$\vec{H}_{general}$ forces the user to select three values satisfying \cref{railangle}: $\rho$, $r_{\rho}$, and $d_{\rho}$.

@@

This syntax just represents the Euclidean distance between vertices. Thus:
\begin{equation}
%%  \text{one-hop} &= dist(\vec{H}_{general}(0,0,\rho,d_{\rho}),\vec{H}_{general}(0,1,\rho,d_{\rho},r))  \\  
%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r\sin(0) - r\sin(\rho/3+1\cdot\frac{2\pi}{3}))^2  +
%%    (r\cos(0) - r\cos(\rho/3 + 1\cdot\frac{2\pi}{3}))^2} \\
%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r\sin(\rho/3 + \frac{2\pi}{3}))^2  +
%%    (r - r\cos(\rho/3 + \frac{2\pi}{3}))^2} \\
%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r^2\sin^2(\rho/3 + \frac{2\pi}{3})  +
%%    r^2(1 - \cos(\rho/3 + \frac{2\pi}{3}))^2} \\
  %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.
  \text{one-hop}  = \sqrt{\frac{d_{\rho}^2}{9} + r^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \text{\qquad where: \qquad}   d_{\rho}^2 = 1 - 4 r^2 (\sin( \rho / 2)^2.
\end{equation}
%% so we substitute:
%% \begin{align*}
%%   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.  
%%   \text{one-hop}  &= \sqrt{\frac{1}{9}  + r^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \text{.}\\
%%   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.    
%% \end{align*}
By similar algebra and trigonometry:
\begin{equation}
  \text{two-hop}  = \sqrt{\frac{4 d_{\rho}^2}{9} +  r^2(\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \text{.}\\
\end{equation}
By definition of minimax edge length optimality \cref{eq:optdef}, we are trying to minimize:
\[
R(T(r)) = \frac{\max{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}}{\min{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}} \text{.}
\]
But since $\text{two-hop}(r) \geq \text{one-hop}(r)$, this is equivalent to:
\[
R(T(r)) =  \frac{   \max \{1,\text{two-hop}(r)\}}
      {   \min \{1,\text{one-hop}(r)\}} \text{.}
\]
This quantity will be equal to one of:
\begin{equation}
  \frac{\text{two-hop}(r)}{1},
\frac{1}{\text{one-hop}(r)},
\frac{\text{two-hop}(r)}{\text{one-hop}(r)} \text{.}
\label{eq:ratioset}
\end{equation}
We know that both one-hop($r$) and two-hop($r$) increase monotonically and continuously with increasing $r$.
By inspection, it seems likely that we will minimize this set by equating $\text{one-hop}(r)$ or $\text{two-hop}(r)$
to 1, but to be absolutely sure and to decide which one, we must examine the partial derivative of the ratio
 $\frac{\text{two-hop}(r)}{\text{one-hop}(r)}$ in this range.

@@

Let:
\begin{equation}
  f_{\rho} = -\frac{4 (\sin^2( \rho / 2))}{9} \text{,}
  \end{equation}
\begin{equation}
  g_{\rho} = -\frac{16 (\sin^2( \rho / 2))}{9} \text{,}
\end{equation}
\begin{equation}
  j_{\rho} = \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2 \text{,}
\end{equation}
and:
\begin{equation}
  k_{\rho} = \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2 \text{.}
\end{equation}
Then:
\begin{equation}
  \begin{split}
  \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}  &=
  \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ k_{\rho})}}
       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+j_{\rho}) }} \text{.}
  \end{split}       
\end{equation}
  By inspection of the graph of the derivative of this ratio rendered in \cref{fig:partialderivativediagram}
  observe that the partial derivative of this with respect to
radius $r$ is always negative, for any $\rho \leq \rho_{bc}$.

@@

Therefore, one decreases the minimax length
of the whole system as the radius increases
up to the point that the shorter, one-hop distance is equal to the rail-length, $1$.
In order to optimize the whole system so long as $\rho \leq \rho_{bc}$,
equate one-hop to $1$ to find the optimum radius:
\begin{equation}
  1 =  \sqrt{
      \frac{1}{9}   +   r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} \; \;+ \sin^2(\rho/3+ \frac{2\pi}{3}) + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2) 
    }
\end{equation}    
from which it follows that:
\begin{equation}
  r_{opt} = \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }} \text{ .} \numberthis  \label{eqrhoopt}
\end{equation}
This leads to a formula for $ d_{opt} $ computed from $\rho, r_{opt}$ via the rail angle equation \cref{railangle}:
\begin{equation}
  %%  d_{opt}^2 &= 1 - 4 (\frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }})^2 (\sin{ \rho / 2})^2   \\
  d_{opt}^2 = 1 - 4 (r_{opt})^2 (\sin{ \rho / 2})^2,
\end{equation}
which is expanded to:
\begin{equation}
%%  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
  d_{opt}^2 = 1 - \frac{16(\sin{ \rho / 2})^2}{\frac{9}{2} ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
\end{equation}
and then rewrite:
\begin{equation}
%%  d_{opt}^2 &= 1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
    d_{opt} = \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + \frac{9}{2} ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}  \text{ .}  \numberthis  \label{dopt}  \\      
\end{equation}
Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, one can
construct a minimax optimal tetrahelix where $0 \leq \rho \leq \rho_{bc}$.
%% Add here references to these equations.
\end{proof}

@@

\begin{corollary}
  The equitetrabeam with minimum maximum edge ratio is produced by $\vec{H}_{general}$ when $ r = \sqrt{\frac{8}{27}} $ and the longest member is $\frac{2}{\sqrt{3}}$,
  which is less than $16\%$ longer
  than the shortest member.
\end{corollary}
